\documentclass{acm}

\usepackage{fontawesome}
\usepackage{etoolbox}
\usepackage{textcomp}
\usepackage[nodisplayskipstretch]{setspace}
\usepackage{xspace}
\usepackage{verbatim}
\usepackage{multicol}
\usepackage{soul}
\usepackage{attrib}

\usepackage{amsmath,amssymb,amsthm}

\usepackage[linesnumbered,commentsnumbered,ruled,vlined]{algorithm2e}
\newcommand\mycommfont[1]{\footnotesize\ttfamily\textcolor{blue}{#1}}
\SetCommentSty{mycommfont}
\SetKwComment{tcc}{ \# }{}
\SetKwComment{tcp}{ \# }{}

\usepackage{siunitx}

\usepackage{tikz}
\usepackage{pgfplots}
\usetikzlibrary{decorations.pathreplacing,calc,arrows.meta,shapes,graphs}

\AtBeginEnvironment{minted}{\singlespacing\fontsize{10}{10}\selectfont}
\setmainfont{Open Sans Light}
\usefonttheme{serif}

\makeatletter
\patchcmd{\beamer@sectionintoc}{\vskip1.5em}{\vskip0.5em}{}{}
\makeatother

% Math stuffs
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\lcm}{\text{lcm}}
\newcommand{\Inn}{\text{Inn}}
\newcommand{\Aut}{\text{Aut}}
\newcommand{\Ker}{\text{Ker}\ }
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}

\newcommand{\yournewcommand}[2]{Something #1, and #2}

\newenvironment{question}[1]{\par\textbf{Question #1.}\par}{}

\newcommand{\pmidg}[1]{\parbox{\widthof{#1}}{#1}}
\newcommand{\splitslide}[4]{
    \noindent
    \begin{minipage}{#1 \textwidth - #2 }
        #3
    \end{minipage}%
    \hspace{ \dimexpr #2 * 2 \relax }%
    \begin{minipage}{\textwidth - #1 \textwidth - #2 }
        #4
    \end{minipage}
}

\newcommand{\frameoutput}[1]{\frame{\colorbox{white}{#1}}}

\newcommand{\tikzmark}[1]{%
\tikz[baseline=-0.55ex,overlay,remember picture] \node[inner sep=0pt,] (#1)
{\vphantom{T}};
}

\newcommand{\braced}[3]{%
    \begin{tikzpicture}[overlay,remember picture]
        \draw [thick,decorate,decoration={brace,raise=1ex,amplitude=4pt},blue] (#2.south west-|T1.south west) -- node[anchor=west,left,xshift=-1.8ex,text=olive]{#3} (#1.north west-|T1.south west);
    \end{tikzpicture}
}

\title{Matrix: An open network for secure, decentralized communication}
\author{Sumner Evans}
\date{August 31, 2021}
\institute{Beeper}

\begin{document}

\begin{frame}{A bit about me}
    \begin{itemize}
        \item I graduated in 2018 with my bachelor's in CS from Mines.
        \item I graduated in 2019 with my master's in CS, also from Mines.
        \item I worked at The Trade Desk for two years right after graduating.
        \item I currently am teaching \textit{CSCI 400 Principles of Programming
            Languages} and I have previously taught \textit{CSCI 406 Algorithms}
            and \textit{CSCI 564 Advanced Computer Architecture}.
        \item I started at Beeper in July.
    \end{itemize}
\end{frame}

\begin{frame}{A bit about you}
    I'd like to get to know everyone a bit more and get a feel for everyone's
    experience levels.
    \pause

    \begin{itemize}[<+->]
        \item How many of you have taken Algorithms?
        \item How many of you have taken Data Structures?
        \item How many of you have taken Intro to Computer Science?
        \item How many of you are in the ACM Matrix chat?
    \end{itemize}
\end{frame}

\begin{frame}{Overview}
    \setbeamertemplate{section in toc}[sections numbered]
    \tableofcontents[hideallsubsections]
\end{frame}

\section{Why Matrix?}

\begin{frame}{Let's talk about chat platforms\ldots}
    Which of the following chat networks do you use/have you used?
    \begin{itemize}[<+->]
        \item TikTok
        \item Snapchat
        \item Instagram
        \item Discord
        \item Facebook Messenger
        \item iMessage
        \item Hangouts
        \item Slack
        \item Signal
        \item Telegram
        \item Wire
    \end{itemize}
    \pause[\thebeamerpauses]
    What do all of these chat networks have in common?
    \pause

    They are \textbf{non-interoperable, and many are closed source and/or
    unencrypted}.
\end{frame}

\begin{frame}{Why is this a problem?}
    The \textbf{closed source} platforms are problematic because you can never
    be sure \textit{how your data is being used}.
    \pause

    The \textbf{unencrypted} platforms are problematic because your messages are
    not private.
    \pause

    And, because none of them are interoperable, you have to have a ton of chat
    apps on your phone.
\end{frame}

\end{document}
% Local Variables:
% TeX-command-extra-options: "-shell-escape"
% End:
